---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# geoflowr

The goal of geoflowr is to ...

## Installation

You can get the most recent version of geoflowr from [Github](https://github.com/ropenscilabs/geoflowr)  and install with:

``` r
devtools::install_github("ropenscilabs/geoflowr")
```

## The Problem

We are hopeing to plot spatial flows using `ggplot2` and then using `gganimate` to show changes through time. There are many ways to do this ouside `ggplot2` and there is already a `geom_curve()` functionthat creates a plot similar    


### Example Dataset

```{r data, fig.width=12, message=FALSE, warning=FALSE}

library(ggplot2)
library(readr)
library(dplyr)
library(sf)

coords <- read_csv('data-raw/world.csv') %>% 
  filter(!is.na(admin)) %>%
  select(admin,
         x = Longitude, 
         y = Latitude)

flows <- read_csv('data-raw/201802.csv') %>%
  select(year,
         period,
         reporter,
         partner,
         netweight_kg)
  
src <- coords %>%
  rename(reporter = admin)
dst <- coords %>% 
  rename(partner = admin)

# join coords to src and dst

df <- flows %>%
  left_join(src, by = 'reporter') %>%
  left_join(dst, by = 'partner', suffix = c('_src','_dst')) %>%
  filter(complete.cases(.))

world1 <- sf::st_as_sf(maps::map('world', plot = FALSE, fill = TRUE))

```



### Current ggplot implimentation - geom_curve()


```{r geom_curve}

ggplot(df) + 
  geom_sf(data = world1) +
  geom_curve(aes(x = x_src, y = y_src, xend = x_dst, yend = y_dst, size = log10(netweight_kg)),
             #curvature = 0.75, angle = -45,
             arrow = arrow(length = unit(0.25,"cm"))) +
  theme_minimal()


```




